\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{hyperref}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{fontawesome}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Garvit Joshi}}\\
	Bengaluru $\cdot$ \href{mailto:garvitjoshi9@gmail.com}{garvitjoshi9@gmail.com} $\cdot$ \href{tel:7983856395}{7983856395} $\cdot$ \href{https://garvit-joshi.github.io}{\faBriefcase} $\cdot$ \href{https://www.linkedin.com/in/garvitjoshi9/}{\faLinkedin} $\cdot$ \href{https://github.com/garvit-joshi/}{\faGithub}\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Lovely Professional University}\hfill Jalandhar, Punjab\\
Bachelor of Technology Computer Science, \textit{GPA: 7.77} \hfill Aug 2018 - Jul 2022\\
\vspace{2mm}
\textbf{St. Anthony Sr. Sec. School}\hfill Fatehgarh, Uttar Pradesh\\
XII, Physics, Chemistry, Maths, Computer Science \textit{Percentage: 66.6\%} \hfill May 2017 - Jun 2018\\
\vspace{2mm}
\textbf{St. Thresa Sr. Sec. School}\hfill Nainital, Uttarakhand\\
X, \textit{Percentage: 68.4} \hfill May 2015 - Jun 2016\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{MoveInSync} \hfill Bengaluru, Karnataka\\
\textit{Software Engineer} \hfill May 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Contributed to the Vehicle Optimization team, automating employee commute to the office while maximizing cab utilization.
	\item Collaborated on automating point of interest setup for new clients, streamlining onboarding processes and enhancing client satisfaction.
	\item Implemented a dynamic employee scheduling solution utilizing a genetic algorithm to optimize workforce allocation for clients, effectively reducing mobility costs.
	\item Collaborated on developing a Configuration Service allowing clients to select routing algorithms for employee management.
\end{itemize}
\textbf{MoveInSync} \hfill Bengaluru, Karnataka\\
\textit{Software Engineer-Intern} \hfill Oct 2021 - Apr 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Enhanced UI Automation Suite, elevating pass rates from 40\% to 75\%.
	\item Integrated JPA and In-Memory Caching into microservices, boosting application stability by 5\% and improving performance by up to 30\%.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	AWS:                  & AWS S3, EC2, Route 53, AWS SDK                                            \\
	Java:                 & Java 8 - 21, Virtual Threads, Thread Pool Executors, Reactive Programming \\
	Spring Boot:          & Spring Data JPA, Spring Security, jOOQ, Spring Reactive Web, JDBC         \\
    Tools and Framwork:   & Redis, Apache Kafka, PostgreSQL, Amazon Redshift, Amazon DynamoDB         \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Mailing Service}} {\sl Java 17, Spring Boot 3.x} \hfill \href{https://github.com/AWS-Cloud-Community-LPU/mailing-service}{\faGithub}\\
Founded and led AWS Cloud Community-LPU during college, creating an official mailing engine and registration system to enhance communication and event coordination, leveraging AWS cloud services, and achieving measurable community growth and engagement.\\
\vspace*{2mm}
{\textbf{Redux}} {\sl C++ 11, CMake} \hfill \href{https://github.com/garvit-joshi/Redux}{\faGithub}\\
Developed a C++ cross-platform application to securely store user data with AES 256-bit encryption.\\
\vspace*{2mm}
{\textbf{Iron Hide}} {\sl Java 21, Spring Boot 3.x, PostgreSQL, Virtual threads, Kafka} \hfill \href{https://github.com/garvit-joshi/ironhide}{\faGithub}\\
Designed and developed a robust auditing service for seamless integration with Kafka and controllers. The service, implemented in Java 21 and powered by Spring Boot 3.x, leverages PostgreSQL for data storage. Virtual threads enhance performance and scalability.\\
\vspace*{2mm}
{\textbf{Ada}} {\sl Python, RSS Feed parser} \hfill \href{https://github.com/AWS-Cloud-Community-LPU/Ada\_TelegramBot}{\faGithub}\\
A Telegram bot hosted on AWS EC2 that broadcasts AWS Infrastructure news from the official AWS RSS feed to a Telegram group, featuring caching and logging functionalities for enhanced performance and monitoring.\\
\vspace*{2mm}
{\textbf{Aster}} {\sl Python, TelegramBot} \hfill \href{https://github.com/garvit-joshi/Aster_TelegramBot}{\faGithub}\\
Aster, all-in-one solution for WazirX crypto exchange analysis on Telegram.\\
Custom Alerts: Set personalized alerts for specific crypto assets, ensuring you never miss out on crucial market movements.\\
\vspace*{2mm}
{\textbf{Bhagavad Gita}} {\sl Laravel, PHP, PostgreSQL} \hfill \href{https://github.com/garvit-joshi/Bhagavad-Gita}{\faGithub}\\
Designed and developed a comprehensive Laravel project encompassing both frontend and backend components, utilizing a PostgreSQL database\\
\vspace*{2mm}
\ 
\end{document}
